---
title: "Format of contact matrices"
author: "Joel Barnes"
date: '`r format(Sys.time(), "%B %d, %Y %H:%M:%S")`'
output: 
  html_document:
    toc: true
    number_sections: true
    toc_float: true
    toc_depth: 5
    code_folding: show
editor_options:
  chunk_output_type: console
---

<style>
  html, body { font-size: 14px; }
  p { margin-bottom: 18px; }
  h1 { margin-top: 30px; font-size: 1.75rem; }
  h1.title {font-size: 2rem;  }
  h2 { font-size: 1.35rem; margin-top: 30px; }
  h3 { font-size: 1.15rem; margin-top: 30px; }
  h4 { font-size: 1.05rem; margin-top: 30px; }
  h4.date { margin-top: 0; margin-bottom: 3rem; }
  p.caption { margin-top: 2rem; }
  img { width: 100%; height: auto; }
  blockquote { border-left: 5px solid #af3c43; border-bottom: 1px solid #efefef; font-weight: normal; font-size: 1rem; }
  .dataTables_filter, .dataTables_length {font-weight: normal; }
  div.main-container { width: 100% !important; max-width: 100% !important; margin-left: auto; margin-right: auto; }
  td.dt-top { vertical-align: top; }
  .level3 h3, .level4 h4 { color: #337ab7; font-weight: bold; }
  .level4 h4 { margin-top: 96px; }
  li > img { margin-top: 24px; margin-bottom: 24px; }
</style>

<img src="https://www.statcan.gc.ca/wet-boew4b/assets/sig-blk-en.svg" style = "max-width: 300px; height: auto; margin-bottom: 24px;" alt="logo">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, dpi = 300)
```

# Load packages to extend base R

```{r}
library(DT)
```

# Load contact matrices

```{r}
load(url("https://github.com/barnzilla/covid19-agestructureSEIR-wuhan-social-distancing/blob/master/data/contacts.Rdata?raw=true"))
```

# Structure of the contact matrices

```{r}
str(contacts)
```

# Contact matrices for Canada
## Home

```{r}
datatable(contacts$CAN$home)
```

## Work

```{r}
datatable(contacts$CAN$work)
```

## School

```{r}
datatable(contacts$CAN$school)
```

## Others

```{r}
datatable(contacts$CAN$others)
```

## All

```{r}
datatable(contacts$CAN$all)
```